---
output: github_document
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
devtools::load_all()
```

# General Bikeshare Feed Specification - R Package

*Developed by Kaelyn M. Rosenberg (author) and Simon P. Couch (author, maintainer)*

![CRAN Badge](http://www.r-pkg.org/badges/version/{gbfs}) [![Build Status](https://travis-ci.org/ds-civic-data/gbfs.svg?branch=master)](https://travis-ci.org/ds-civic-data/gbfs)

The `gbfs` package supplies a set of functions to interface with General
Bikeshare Feed Specification .json feeds in R, allowing users to save
and accumulate tidy .rds datasets for specified cities/bikeshare programs.

__Features__

* Get bikeshare data by specifying city or supplying url of feed
* All feeds for a city can be saved with a single function
* New information from dynamic feeds can be appended to existing datasets

## Installation

We're now on CRAN! Install the latest release, 1.1.0, with:

```{r cran-installation, eval = FALSE}
install.packages("gbfs")
library("gbfs")
```

You can install the development version of `gbfs` from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ds-civic-data/gbfs")
```

## Example

Here the function `get_gbfs()` is used to create a folder and save all existing
gbfs .json feeds for Portland. Then `get_station_status()` is used to append the
most recent version of the station status .json feed to the station status .rds
dataset.

Note: Throughout this example I use a temporary directory by calling `withr::with_dir(tempdir(), ...)` as the codes are examples. In real life, we would skip the temporary directory stuff; just focus on the `...` for the purpose of this tutorial.

```{r example}
withr::with_dir(tempdir(), get_gbfs(city = "Portland", feeds = "all", directory = "pdx_gbfs"))
withr::with_dir(tempdir(), list.files("pdx_gbfs"))
station_status <- withr::with_dir(tempdir(), readRDS("pdx_gbfs/station_status.rds"))
head(station_status)
nrow(station_status)
withr::with_dir(tempdir(), get_station_status(city = "Portland", directory = "pdx_gbfs", file = "station_status.rds"))
station_status <- withr::with_dir(tempdir(), readRDS("pdx_gbfs/station_status.rds"))
nrow(station_status)
```
