---
output: github_document
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
devtools::load_all()
```

# General Bikeshare Feed Specification - R Package

[![Travis-CI Build Status](https://travis-ci.org/ds-civic-data/gbfs.svg?branch=master)](https://travis-ci.org/ds-civic-data/gbfs)

The `gbfs` package supplies a set of functions to interface with General
Bikeshare Feed Specification .json feeds in R, allowing users to save
and accumulate tidy .rds datasets for specified cities/bikeshare programs.

__Features__

* Get bikeshare data by specifying city or supplying url of feed
* All feeds for a city can be saved with a single function
* New information from dynamic feeds can be appended to existing datasets

## Installation

You can install gbfs from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("ds-civic-data/gbfs")
```

## Example

Here the function `get_gbfs()` is used to create a folder and save all existing
gbfs .json feeds for Portland. Then `get_station_status()` is used to append the
most recent version of the station status .json feed to the station status .rds
dataset.

```{r example}
get_gbfs(city = "Portland", feeds = "all", directory = "pdx_gbfs")
list.files("pdx_gbfs")
station_status <- readRDS("pdx_gbfs/station_status.rds")
head(station_status)
nrow(station_status)
get_station_status(city = "Portland", directory = "pdx_gbfs", file = "station_status.rds")
station_status <- readRDS("pdx_gbfs/station_status.rds")
nrow(station_status)
```
