---
title: "Exploring Basic Functionality with Kansas City, Missouri's `B-Cycle`"
author: "Simon P. Couch"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{KCMO Example}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this example, we'll load `gbfs` into the environment and then explore some of the basic functionality of the package using Kansas City, Missouri's `B-Cycle` program as an example.

```{r}
devtools::load_all()
```

Note: Throughout this vignette I use a temporary directory by calling `withr::with_dir(tempdir(), ...)` as this is a vignette and the codes are examples. In real life, we would skip the temporary directory stuff; just focus on the `...` for the purpose of this tutorial.

We'll start by using the `get_gbfs` function--this is generally a good starting place. `get_gbfs` can find and grab all of the feeds for a specified city and save them in a folder as tidy .rds datasets. For the `city` argument, supply `get_gbfs` with either the url to KCMO's gbfs.json file (at `https://gbfs.bcycle.com/bcycle_kc/gbfs.json`) or a character string with the name of the city. Here, we'll use the name of the city. Notice we did not supply an argument for `feeds`, so the function will default to grabbing all of the feeds that it finds exists.

```{r}
withr::with_dir(tempdir(), get_gbfs(city = "kansas city", directory = "kc_bikeshare"))
```

```{r}
withr::with_dir(tempdir(), dir("kc_bikeshare"))
```

Here, it looks like Kansas City, in addition to the required .json feeds, supplies `system_pricing_plans` and `system_regions`. The only 'dynamic' feed, (i.e. feed that changes regularly) supplied is the required `station_status`. Let's take a look at `station_status`.

```{r, echo = FALSE}
station_status <- withr::with_dir(tempdir(), readRDS("./kc_bikeshare/station_status.rds"))
```

```{r}
str(station_status)

nrow(station_status)
```

Here, we see that there are currently 42 rows in station status. There are also plenty of interesting columns, such as the station ID, the number of bikes available currently, etc. As I write this, a few minutes have passed since I called `get_gbfs`. We can now call `get_gbfs` again, with slightly different arguments, so that we can append rows to the `station_status` dataset but keep the static files unchanged.

```{r}
withr::with_dir(tempdir(), get_gbfs(city = "kansas city", 
                                    directory = "kc_bikeshare", 
                                    feeds = "dynamic"))
```

Reading the dataset in again and calling `nrow`, we can see that the number of rows doubled.

```{r}
station_status <- withr::with_dir(tempdir(), readRDS("./kc_bikeshare/station_status.rds"))

nrow(station_status)
```

In the dataset, there are now two entries for each station—running this function many times over time could allow for the tracking of many interesting variables of time. In a few lines, there is already plenty to explore.

In combination with cron or task scheduler, depending on your operating system, this set of functions can be used to quickly build up informative datasets about bikeshare programs in a user's town of interest.